# Nifti to BIDS Conversion

## Reorganise the Nifti Files

At this point, the data is still messy.
For a reusable and sharable format (and to be able to use it with some existing toolboxes), I rearranged the nifti data into the [BIDS](https://bids.neuroimaging.io/) format.
I tried to automate this process as much as possible, however the raw data was unstructured in different ways across participants in certain cases.
Therefore, instead of writing 19 specialised versions of the code, I carried out some manual steps (e.g. moving structural scans from one folder to another).
Running the code provided below on the raw data alone will not put the data into the BIDS format like you see it on the server.

The following example structure was created after taking the steps above.

```
sub-01
│
└───func
│   │   sub-01_task-train_run-1_sbref.json
|   |   sub-01_task-train_run-1_sbref.nii
│   │   sub-01_task-train_run-1_bold.json
|   |   sub-01_task-train_run-1_bold.nii
|   |   ...
│   │   sub-01_task-test_run-16_sbref.json
|   |   sub-01_task-test_run-16_sbref.nii
│   │   sub-01_task-test_run-16_bold.json
|   |   sub-01_task-test_run-16_bold.nii
|
└───anat
|   │   sub-01_T1w.json
|   │   sub-01_T1w.nii
|
└───fmap
|   |   sub-01-magnitude1.json
|   |   sub-01-magnitude1.nii
|   |   sub-01-magnitude2.json
|   |   sub-01-magnitude2.nii
|   |   sub-01-phasediff.json
|   |   sub-01-phasediff.nii
 ```

*Extra Note*: Some participants have fieldmaps while others don't. When available, I used them, and otherwise they are ignored

```{r}
#| class-output: "sourcecode python"

cat(readLines("src_implied_motion/src/Py/format_bids.py"),sep = "\n")
```

## Create Events Files

To create the event files used in my GLM, I used the following code below, which create one `.tsv` file per functional run and saves it under the relevant subject's func folder in the `data/bids`.
For the decoding, we tried two different kinds of design matrices. The examples for the two kind are:

If `expanded==False`, a table of the following type is created:

| onset | duration | motion direction |
|-------|----------|------------------|
| 10  | 15      | left             |
| 30   | 15      | forward          |
| ...   | ...      | ...              |

If `expanded==True`, a table of this type is created:

| onset | duration | motion direction |
|-------|----------|------------------|
| 10  | 15      | left_1             |
| 30   | 15      | forward_1          |
| 50 | 15 | left_2 |
| ...   | ...      | ...              |



```{r}
#| class-output: "sourcecode python"

cat(readLines("src_implied_motion/src/Py/prepare_events.py"),sep = "\n")
```